%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Main Author} % Role
    {Internet of Things in Five Days (book)} % Title
    {On-line} % Location
    {Jul. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Theory and hands-on examples to develop Internet of Things (IoT) applications using IPv6, 6LoWPAN, Contiki OS and Zolertia platforms.}
        \item {Examples include wireless networking on UDP/TCP, MQTT, CoAP, RPL and Radio basics.}
        \item {The publication of its two releases was sponsored by the Abdus Salam International Centre of Theoretical Physics (ICTP) in Italy (Mar. 2015) and the Pontificia Universidad Javeriana in Colombia (Jul. 2016).}
        \item {The book has been translated to Spanish and French by external collaborators and Universities.}
        \item {The book is Open Source and released for non-commercial purposes as teaching material.}
        \item {Available online at: https://github.com/alignan/IPv6-WSN-book.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {First Speaker} % Role
    {Reconfigurable IPv6-enabled wireless sensor network for urban monitoring and street light control in city environments (paper)} % Title
    {Smart City Expo World Congress, Barcelona-Spain} % Location
    {Nov. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Presented the results of the joint efforts made by Advancare S.L and Orange Labs R+D Spain to develop an intelligent test bed for Smart Cities solutions.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
